What We Eval in the Shadows

### 2021-04-13 paper/main.tex
Explain why it is more than 100% for some tables

\begin{table}[h]\centering\small
\begin{minipage}{4cm}
  \begin{tabular}{r|r|r}\hline
 Environment & \#sites & \%sites \\\hline
 Function & \packageNbFunctionEnvSites &  \packageNbFunctionEnvSitePercent\\
 Synthetic & \packageNbSyntheticEnvSites & \packageNbSyntheticEnvSitePercent \\
 Global &  \packageNbStrictGlobalEnvSites & \packageNbStrictGlobalEnvSitePercent \\
 Package & \packageNbPackageNamespaceEnvSites & \packageNbPackageNamespaceEnvSitePercent \\\hline
\end{tabular}
\caption{Environments per site} \label{tab:highlevelenvironments}
\end{minipage} \hspace{1cm}
\begin{minipage}{3.7cm}\centering
\begin{tabular}{r|r|r}\hline
 Offset & \#sites & \%sites \\\hline
  \packageCallerEnvHierarchyNamea & \packageCallerEnvHierarchySitesaRnd & \packageCallerEnvHierarchySitePercenta \\
  \packageCallerEnvHierarchyNameb& \packageCallerEnvHierarchySitesbRnd & \packageCallerEnvHierarchySitePercentb \\
  \packageCallerEnvHierarchyNamec& \packageCallerEnvHierarchySitescRnd & \packageCallerEnvHierarchySitePercentc  \\
  > 3& \packageNbFarAwayCallerSites &  \packageNbFarAwayCallerSitePercent \\\hline
 \end{tabular}
\caption{Function offset}\label{tab:funoffset}
\end{minipage}\hspace{1cm}
\begin{minipage}{3.8cm}
\begin{tabular}{r|r|r} \hline
Parent & \#sites & \%sites \\\hline
Function & \packageNewEnvCategorySitesa & \packageNewEnvCategorySitePercenta \\
Package & \packageNewEnvCategorySitesb &  \packageNewEnvCategorySitePercentb\\
Global & \packageNewEnvCategorySitesc & \packageNewEnvCategorySitePercentc \\
Empty & \packageNewEnvCategorySitesd & \packageNewEnvCategorySitePercentd \\\hline
\end{tabular} \label{tab:newenvs}
\caption{Wrapper envs.}
\end{minipage}
\end{table}
One site could appear in several categories. However, most sites, \ie \packageNbOneCategoryEnvirSitePercent, have only kind of the above environments passed to them.

@@

\begin{compactitem}[---]
\item {\it Promise:} Function arguments are passed as promises, suspended
  computations, from a promise one can retrieve the source expression with a
  call to the \c{substitute} function.
\item {\it Reflection:} The \c{match.call} function reflectively captures
  the expression that called the current function.
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote} and \c{expression} functions.
\item {\it String:} Finally, expressions can be created from strings by invoking
  one of \c{parse}, \c{str2expression} and \c{str2lang}.
\end{compactitem}

>>>>

\begin{table}[h]
\centering
\small
\begin{minipage}{4cm}
  \begin{tabular}{r|r|r}\hline
 Environment & \#sites & \%sites \\\hline
 Function & \packageNbFunctionEnvSites &  \packageNbFunctionEnvSitePercent\\
 Synthetic & \packageNbSyntheticEnvSites & \packageNbSyntheticEnvSitePercent \\
 Global &  \packageNbStrictGlobalEnvSites & \packageNbStrictGlobalEnvSitePercent \\
 Package & \packageNbPackageNamespaceEnvSites & \packageNbPackageNamespaceEnvSitePercent \\\hline
\end{tabular}
\caption{Environments per site} \label{tab:highlevelenvironments}
\end{minipage} \hspace{1cm}
\begin{minipage}{3.7cm}\centering
\begin{tabular}{r|r|r}\hline
 Offset & \#sites & \%sites \\\hline
  \packageCallerEnvHierarchyNamea & \packageCallerEnvHierarchySitesaRnd & \packageCallerEnvHierarchySitePercenta \\
  \packageCallerEnvHierarchyNameb& \packageCallerEnvHierarchySitesbRnd & \packageCallerEnvHierarchySitePercentb \\
  \packageCallerEnvHierarchyNamec& \packageCallerEnvHierarchySitescRnd & \packageCallerEnvHierarchySitePercentc  \\
  > 3& \packageNbFarAwayCallerSites &  \packageNbFarAwayCallerSitePercent \\\hline
 \end{tabular}
\caption{Function offset}\label{tab:funoffset}
\end{minipage}\hspace{1cm}
\begin{minipage}{3.8cm}
\begin{tabular}{r|r|r} \hline
Parent & \#sites & \%sites \\\hline
Function & \packageNewEnvCategorySitesa & \packageNewEnvCategorySitePercenta \\
Package & \packageNewEnvCategorySitesb &  \packageNewEnvCategorySitePercentb\\
Global & \packageNewEnvCategorySitesc & \packageNewEnvCategorySitePercentc \\
Empty & \packageNewEnvCategorySitesd & \packageNewEnvCategorySitePercentd \\\hline
\end{tabular} \label{tab:newenvs}
\caption{Wrapper envs.}
\end{minipage}

\vspace{-0.3cm} \begin{minipage}{\textwidth} \footnotesize
One site could appear in several categories. However, most sites, \ie \packageNbOneCategoryEnvirSitePercent, have only kind of the above environments passed to them.
\end{minipage}
\end{table}

@@

\begin{compactitem}[---]
\item {\it Reflection:} The \c{match.call} function reflectively captures
  the expression that called the current function.
\item {\it Constructed:} Expressions can be constructed by invoking the
  \c{quote}, \c{enquote}, \c{expression} and \c{substitute} functions. Function arguments are passed as promises, suspended computations, and  \c{substitute} is sometimes used to retrieve the source expression associated to the promise.
\item {\it String:} Finally, expressions can be created from strings by invoking
  one of \c{parse}, \c{str2expression} and \c{str2lang}.
\end{compactitem}
